---
title: "1. Installation"
author: "Adam T. Kocsis"
date: '`r Sys.Date()`'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{1. Installation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(via)
```


## Stable version from the CRAN

The stable version of the package is available on [CRAN servers](https://cran.r-project.org/package=via), which means that you can install it with the regular `install.packages()` function.

```{r cran, eval=FALSE}
install.packages("via")
```

If for some reason, the installlation from CRAN fails, you might need to look into alternative methods.


* * * 

## Alternative methods

#### Development version

If you encounter technical problems with the package that are not described anywhere, you might want to take a look at the [development version](https://github.com/adamkocsis/via/tree/devel).

If you wish to install the development version, I recommend a manual installation:  
1. Clone the repository to your local hard drive.  
2. Open a terminal and navigate to the directory where you cloned. The `via` directory should be visible from there.  
3. Run this line in the terminal  

```
R CMD INSTALL via 
```

- *If you see an error suggesting that `R` is not found, you have to add it to your `PATH` environmental variable.*  
- *If the R packages that `via` depend on are not installed, you have to install them manually, or you will get an error.*

